Introductory statistics with `intRo`

### 2016-02-11 jcgs-paper-2016/paper.Rmd
Finish heike's edits

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/ui_annotate.pdf}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure*}
 1. **Top Navigation** - The top navigation bar includes two sets of buttons. The left-aligned buttons are informational buttons. The first is a link to \texttt{intRo}. The second is a link to this documentation page. The third is a link to the GitHub repository where the code for \texttt{intRo} is housed. The final button is a link to our websites, which contain contact information if there are any questions or comments. The right-aligned buttons are \texttt{intRo} utilities. The first is a button to toggle the visibility of the code panel (5). The last is a button to print the stored module results, and the associated code (if visible).
 2. **Side Navigation** - The side navigation panel includes the modules that perform a specific data analysis task.
 3. **Options Panel** - The options panel includes module-specific options which the user can use to customize their results.
 4. **Results Panel** - The results pane displays the result of the selected module and options.
 5. **Code Panel** - The code panel displays the \texttt{R} code used to generate the results from the student's \texttt{intRo} session. The code panel is shown by default to facilitate an interest in coding, but can be hidden by clicking the code toggle button in the Top Navigation bar.

There are seven default modules within \texttt{intRo}, which perform specific data analysis tasks that employ an easy to use point-and-click interface. Each module is placed within a higher level category to further help students navigate the tool. The default modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics - and more modules can easily be added by an instructor, as detailed in section \ref{modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

In addition to making \texttt{intRo} intuitive to use, we've also created a documentation website that is consistent with the interface of the application. The documentation is available at http://gammarama.github.io/intRo and hyperlinked within the application itself. This documentation covers all default modules and makes learning to use \texttt{intRo} even more painless.

\texttt{intRo} has an ulterior motive as well: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well. \texttt{intRo} uses \texttt{rmarkdown}'s [@rmarkdown] \texttt{render} function in order to print the results, by dymanically executing the user's \texttt{R} script. By default, the output will include the \texttt{R} code, but if the user elects to hide the source code by clicking the code toggle button at the top, the code will not appear in the printed results.

>>>>

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/ui_annotate.pdf}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure*}
 1. **Top Navigation** - The top navigation bar includes two sets of clickable icons. The left-aligned buttons are informational buttons. The first is a link to \texttt{intRo}. The second is a link to the documentation page. The third is a link to the GitHub repository where the code for \texttt{intRo} is housed. The final button is a link to our websites, which contain contact information if there are any questions or comments. The right-aligned buttons are \texttt{intRo} utilities. The first is a link to toggle the visibility of the code panel (5). The middle icon downloads an rmarkdown [@rmarkdown] document of the analysis performed. The last is a link to print the stored module results, and the associated code (if visible).
 2. **Side Navigation** - The side navigation panel includes a list of data analysis tasks.
 3. **Options Panel** - The options panel includes task-specific options which the user can use to customize their results.
 4. **Results Panel** - The results pane displays the result of the selected module and options.
 5. **Code Panel** - The code panel displays the \texttt{R} code used to generate the results from the student's \texttt{intRo} session. The code panel is shown by default to facilitate a transition to coding, but can be hidden by clicking the code toggle button in the Top Navigation bar.

The modules included in \texttt{intRo} are split into three higher level categories - data, summaries, and statistics. Under each of these categories, there are seven default modules, which perform specific data analysis tasks that employ an easy to use point-and-click interface. More modules can easily be added by an instructor, as detailed in section \ref{modules}. The default modules support uploading and downloading a dataset, transforming variables, graphical and numerical summaries, simple linear regression, contingency tables, and T-tests.

We've also created a documentation website that is consistent with the interface of the application. The documentation is available at http://gammarama.github.io/intRo and hyperlinked within the application itself.

\texttt{intRo} has an ulterior motive as well: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well. \texttt{intRo} uses \texttt{rmarkdown}'s \texttt{render} function in order to print the results, by dymanically executing the user's \texttt{R} script. By default, the output will include the \texttt{R} code, but if the user elects to hide the source code by clicking the code toggle button at the top, the code will not appear in the printed results.
